The Accuracy of KNN, SVM, SVDD, neural network and DBSCAN, k-means for Determining the Cancer by Gene-expression Signatures And the Arrhythmia Types

### 2023-05-27 final/paper/main.tex
fix typo

The source code can be found in \href{https://github.com/OEmiliatanO/CSE\_data\_mining}{here}.

@@

\section{Conclusion}
In this study, we present a framework of algorithm to deal with the dataset containing 
out-of-knowledge data. And with in this algorithm, multiple major machine learning 
techniques are used, e.g., for preprocess, PCA, AE, normalization; for classification, 
KNN, SVM, SVDD, NN, as for clustering, DBSCAN, k-means, NN-chain. Among the various 
combinations, PCA + KNN + k-means performs outstanding in gene expression cancer RNA-Seq 
dataset, and raw data + KNN + k-means performs the best in arrhythmia dataset. Accidently, 
SVM performs bad in these two dataset. The main cause is the defect of the multi-classification 
SVMs design, which make some SVMs hard to separate the target types. However, by customize 
the kernel for each SVMs, the problem may ease. In the same time, the increasing number of 
parameters can be fine-tuned by metaheuristic algorithms, e.g., simulated annealing, genetic 
algorithm, etc. We will develope a refinement design on multi-classification SVMs, to enhance 
the accuracy on these datasets.

>>>>

The source code can be found in \href{https://github.com/OEmiliatanO/CSE\_data\_mining}{https://github.com/OEmiliatanO/CSE\_data\_mining}.

@@

\section{Conclusion}
In this study, we present a framework of algorithm to deal with the dataset containing 
out-of-knowledge data. And with in this algorithm, multiple major machine learning 
techniques are used, e.g., for preprocess, PCA, AE, normalization; for classification, 
KNN, SVM, SVDD, NN, as for clustering, DBSCAN, k-means, NN-chain. Among the various 
combinations, PCA + KNN + k-means performs outstanding in gene expression cancer RNA-Seq 
dataset, and raw data + KNN + k-means performs the best in arrhythmia dataset. Accidently, 
SVM performs bad in these two dataset. The main cause is the defect of the multi-classification 
SVMs design, which make some SVMs hard to separate the target types. However, by customize 
the kernel for each SVM, the problem may ease. In the same time, the increasing number of 
parameters can be fine-tuned by metaheuristic algorithms, e.g., simulated annealing, genetic 
algorithm, etc. We will develope a refinement design on multi-classification SVMs, to enhance 
the accuracy on these datasets.
